Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-03-23 paper/ms.tex
Add stars instead of gas test

@@

>>>>

{\bf \subsection{Stars Instead of Gas}
In the SMUGGLE model considered in this work, we instantaneously added gas to
the $N$-body system after $1.5\,\textrm{Gyr}$ of evolution. One might wonder if
this sudden change to the potential is responsible for the stable pattern speed
evolution. To test whether this is the case, we added mass to the system in the
same way we did for the SMUGGLE model, but using collisionless particles instead
of gas. The result of this experiment is shown in Fig.~\ref{fig:ps-star}. While
there is an offset compared to the pure $N$-body case, we see that the pattern
speed evolution is broadly consistent with a declining pattern speed. This
indicates that the gas phase is responsible for the stable pattern speed.}

@@

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/ps_star.pdf}
    \caption{{\bf Pattern speed evolution of a model in which we instaneously add stars instead of gas to the simulation, with the same density profile as the gas phase. The pattern speed evolution in this case is qualitatively similar to that of the $N$-body case, with a slight offset in the pattern speed. This test demonstrates that the stable pattern speed evolution in the SMUGGLE case is not simply a consequence of the change in potential imposed in our initial conditions.}}
\label{fig:ps-star}
\end{figure}
